---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# qpmadr

<!-- badges: start -->
<!-- badges: end -->


`qpmadr` provides R-bindings to the quadratic programming-solver `qpmad`, written by [Alexander Sherikov](https://github.com/asherikov).

## Installation

You can install the released version of qpmadr from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("qpmadr")
```

## Example


This is an example which shows you how to solve a simple problem:

$$ \min_{\rm x}{ \space x'H x} $$

$$ s.t. \space \sum_{i}{x_i} = n $$

$$ -2 \leq x_i \leq 2 $$

where $H$ is a random positive definite matrix of size $n \times n$, and $x$ is a (column) vector of size $n$.

The code below will run a benchmark against the quadprog solver for n=100, checking that both give the same results.


```{r example}
library(qpmadr)
library(quadprog)
library(microbenchmark)


set.seed(42)

n = 100

H = crossprod(matrix(rnorm(n*n), n))

# constraint specification for qpmadr
lb = -2
ub = 2
A = matrix(1, 1, n)
Alb = n
Aub = n

# constraint specification for quadprog
At = cbind(rep_len(1, n), diag(1, n, n), diag(-1, n, n))
b = c(n, rep_len(-2, 2*n))



bm = microbenchmark(
  check    = "equal",
  qpmadr   = qpmadr::solveqp(H, lb=lb, ub=ub, A=A, Alb=Alb, Aub=Aub)$solution,
  quadprog = quadprog::solve.QP(H, numeric(n), At, b, meq=1)$solution
)


knitr::kable(summary(bm, "relative"), digits=1)
```

Timings are relative.


## C++-interface

The solver is a c++ header-only library and can be used in other packages via the LinkingTo: field

